Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-06 talk/dls2012/paper.tex
some comments from me

\revc{
Don't break code listings across pages, as at the start of section 3.  It makes
them very hard to follow.
}

@@

\revc{
This paper presents an elegant, if simple, technique, and demonstrates that
it's effective in small cases.  The worked example is particularly helpful, and
would be better if it were worked more thoroughly.  Some of the omitted steps
are not entirely obvious, and the paper would be improved by making the
clearer.  In particular, the final program presented on the bottom of page 5,
first column, still has memory access, boxing, and type checks, which the paper
then claims can be removed.  There's enough space to show this.
}

@@

\revc{
Providing source code for the benchmarks measured are needed for others to
reproduce and build on your results.  I believe this should be the minimum
standard for publishing measurements such as these.
}

\revc{
I would have liked to have benchmark results for some larger applications.
When is this optimization effective on a large scale, if ever?
}

@@

\revc{
The discussion of LuaJIT is unsatisfying.  It's not clear to me from that one
quote that Mike is doing the same thing.  It might be worth including LuaJIT in
the benchmarks, and/or examining the actual implementation of LuaJIT.
}

>>>>

\revc{
Don't break code listings across pages, as at the start of section 3.  It makes
them very hard to follow.
}
\cfbolz{let's do that only at the very end, just before submitting}

@@

\revc{
This paper presents an elegant, if simple, technique, and demonstrates that
it's effective in small cases.  The worked example is particularly helpful, and
would be better if it were worked more thoroughly.  Some of the omitted steps
are not entirely obvious, and the paper would be improved by making the
clearer.  In particular, the final program presented on the bottom of page 5,
first column, still has memory access, boxing, and type checks, which the paper
then claims can be removed.  There's enough space to show this.
}
\cfbolz{
we have space now, can someone add the final optimized version of the loop?
}

@@

\revc{
Providing source code for the benchmarks measured are needed for others to
reproduce and build on your results.  I believe this should be the minimum
standard for publishing measurements such as these.
}
\cfbolz{
let's link to the bitbucket source code view. how about we move the benchmarks
to the dls directory as well? or their own repository, we've been using them as
demos
}

\revc{
I would have liked to have benchmark results for some larger applications.
When is this optimization effective on a large scale, if ever?
}
\cfbolz{I don't actually know. Does anybody?}

@@

\revc{
The discussion of LuaJIT is unsatisfying.  It's not clear to me from that one
quote that Mike is doing the same thing.  It might be worth including LuaJIT in
the benchmarks, and/or examining the actual implementation of LuaJIT.
}
\cfbolz{maybe we can look in the new LuaJIT wiki.
how annoying would it be to rerun the benchmarks, if I can find somebody to write them?}
